---
title: An R Markdown document converted from "/Users/godbergodbersen/Desktop/phd_bef_china/may_23/may_23.ipynb"
output: html_document
---

# Data cleaning and creation of new datasets for May 2023

```{r}
library(janitor)
library(tidyverse)
library(readxl)
veg_survey <- read_excel("/Users/godbergodbersen/Desktop/phd_bef_china/phd_bef_china/datas_and_notebooks/2023/may_23/Sapling Survey May 2023.xlsx") |>
  mutate(across(where(is.character), ~str_trim(.) |> tolower())) |>
  clean_names()

sapling_survey <- read_excel("/Users/godbergodbersen/Desktop/phd_bef_china/phd_bef_china/datas_and_notebooks/2023/may_23/Sapling Survey May 2023.xlsx") |>
  mutate(across(where(is.character), ~str_trim(.) |> tolower())) |>
  clean_names()

str(veg_survey)
str(sapling_survey)
```

```{r}
sapling_survey <- sapling_survey |>
  rename("notes" = x21) |>
  mutate(across(where(is.character), ~na_if(., "na")))
sapling_survey
```

## reading in final dataset from september for joining

```{r}
final_data_september <- read.csv("/Users/godbergodbersen/Desktop/phd_bef_china/phd_bef_china/datas_and_notebooks/2023/september_23/final_data_september.csv", stringsAsFactors = FALSE)
str(final_data_september)
```

## Identify missing or ungiven species names and correct spelling mistakes

```{r}
sapling_survey <- sapling_survey |> 
  mutate(
    species = case_when(
      id == "737x" ~ "fern",
      id == "963" ~ "trema cannabina",
      id == "392" ~ "distylium buxifolium",
      species == "444" ~ "clerodendrum cyrtophyllum",
      species == "clerodendrum cyrtophyllum (444)" ~ "clerodendrum cyrtophyllum",
      species == "1171" ~ "lindera reflexa",
      species == "307" ~ "ilex suaveolens",
      species == "1294" ~ "eurya muricata", 
      id == "1294" ~ "eurya muricata", 
      id == "1242" ~ "pterostyrax corymbosus",
      id == "1021" ~ "premna microphylla",
      id == "1217" ~ "camellia fraterna",
      id == "1390" ~ "buddleja lindleyana", 
      species == "?" ~ "unknown sp.", 
      TRUE ~ species
    ),
    species = str_remove_all(species, "\\[|\\]")
  ) |>
  mutate(across(everything(), ~str_replace_all(., "/", ""))) |>
  filter(!is.na(species))

sapling_survey
```

```{r}
sapling_survey <- sapling_survey |>
  mutate(
    # First, set growth_form to "herb" if species is "herb"
    growth_form = case_when(
      str_to_lower(species) == "herb" ~ "herb",
      str_to_lower(species) == "unknown sp." & !is.na(notes) & str_to_lower(notes) == "woody recruit" ~ "shrub/tree",
      TRUE ~ NA_character_
    ),
    # Then, set species to "unknown sp." if it was "herb"
    species = case_when(
      str_to_lower(species) == "herb" ~ "unknown sp.",
      TRUE ~ species
    ),
    # Then, set type for quercus seedling and seedling
    type = case_when(
      str_to_lower(species) == "quercus seedling" ~ "seedling",
      str_to_lower(species) == "seedling" ~ "seedling",
      TRUE ~ NA_character_
    )
  ) |> 
  # Standardize species names
  mutate(
    species = case_when(
      str_to_lower(species) == "alniphylum fortunei" ~ "alniphyllum fortunei",
      str_to_lower(species) == "calicarpa dischotoma" ~ "calicarpa dichotoma",
      str_to_lower(species) == "camellia janopica" ~ "camellia japonica",
      str_to_lower(species) == "clerodendrum cyrtophullym" ~ "clerodendrum cyrtophyllum",
      str_to_lower(species) == "itea" ~ "itea sp.",
      str_to_lower(species) == "lindera erythocarpa" ~ "lindera erythrocarpa",
      str_to_lower(species) == "lindera refelxa" ~ "lindera reflexa",
      str_to_lower(species) == "liquidamabar formosana" ~ "liquidambar formosana",
      str_to_lower(species) == "ltea omeiensis" ~ "itea omeiensis",
      str_to_lower(species) == "mussaendra esquirolii" ~ "mussaenda esquirolii",
      str_to_lower(species) == "musseandra esquirolii" ~ "mussaenda esquirolii",
		  str_to_lower(species) == "musseanda esquirolii" ~ "mussaenda esquirolii",
      str_to_lower(species) == "musseandra equifolia" ~ "mussaenda equifolia",
      str_to_lower(species) == "pterostryax corymbusus" ~ "pterostyrax corymbosus",
		  str_to_lower(species) == "phyllanthus glauca" ~ "phyllostachys glauca",
		  str_to_lower(species) == "camellia chinensis" ~ "camellia sinensis",
      str_to_lower(species) == "quercues serrata" ~ "quercus serrata",
      str_to_lower(species) == "rhapiolepis indica" ~ "rhaphiolepis indica",
      str_to_lower(species) == "rhaphioides indica" ~ "rhaphiolepis indica",
      str_to_lower(species) == "rhalpioides indica" ~ "rhaphiolepis indica",
		  str_to_lower(species) == "rhaipoides indica" ~ "rhaphiolepis indica",
      str_to_lower(species) == "rhododenron simsii" ~ "rhododendron simsii",
      str_to_lower(species) == "rosa" ~ "rosa sp.",
      str_to_lower(species) == "schoepfja jasminodora" ~ "schoepfia jasminodora",
      str_to_lower(species) == "sp 37*" ~ "alniphyllum fortunei",
      str_to_lower(species) == "styrax odoratismus" ~ "styrax odoratissimus",
      str_to_lower(species) == "cfr. styrax odoratissimus" ~ "styrax odoratissimus", 
      str_to_lower(species) == "vaccinium bracetatum" ~ "vaccinium bracteatum",
      str_to_lower(species) == "viburnum sempiverens" ~ "viburnum sempervirens",
      str_to_lower(species) == "araisia crenata" ~ "ardisia crenata",
      str_to_lower(species) == "calicarpa sp" ~ "calicarpa sp.",
      str_to_lower(species) == "calicarpa sp," ~ "calicarpa sp.",
      str_to_lower(species) == "quercus seedling" ~ "quercus sp.",
      str_to_lower(species) == "seedling" ~ "unknown sp.",
      str_to_lower(species) == "woody recruit" ~ "unknown sp.",
		  str_to_lower(species) == "machilus grijsi" ~ "machilus grijesi",
		  str_to_lower(species) == "pterostyrax corymbusus" ~ "pterostyrax corymbosus",
      TRUE ~ species
    )
  )
```

```{r}
sapling_survey <- sapling_survey |>
  mutate(genus = word(species, 1)) |> 
  left_join(final_data_september |> select(genus, family, growth_form) |> distinct(), by = "genus") |> 
  distinct() |>
  mutate(
    growth_form = ifelse(is.na(growth_form.x) | growth_form.x == "", growth_form.y, growth_form.x)
  ) |>
  select(-growth_form.x, -growth_form.y)

sapling_survey
```

## Bring columns into same format as september data and join with september values

```{r}
# Rename columns in sapling_survey to match the format and names of final_data_september
sapling_survey <- sapling_survey |>
  rename(
    number_leaves = leaves,
    number_herb_damaged = herb_dam,
    percent_hmin = hmin,
    percent_hmax = hmax,
    number_fungal_damaged = fpdam,
    percent_fmin = fmin,
    percent_fmax = fmax,
    number_necrotic_damaged = nec_dam,
    percent_nmin = nmin,
    percent_nmax = nmax
  )

# Convert columns to appropriate types
sapling_survey <- sapling_survey |>
  mutate(
    date = as.Date(date),
	month = lubridate::month(date),
    height = as.numeric(height),
    number_leaves = as.numeric(number_leaves),
    number_herb_damaged = as.numeric(number_herb_damaged),
    hprop = as.numeric(hprop),
    percent_hmin = as.numeric(percent_hmin),
    percent_hmax = as.numeric(percent_hmax),
    number_fungal_damaged = as.numeric(number_fungal_damaged),
    fprop = as.numeric(fprop),
    percent_fmin = as.numeric(percent_fmin),
    percent_fmax = as.numeric(percent_fmax),
    number_necrotic_damaged = as.numeric(number_necrotic_damaged),
    nprop = as.numeric(nprop),
    percent_nmin = as.numeric(percent_nmin),
    percent_nmax = as.numeric(percent_nmax)
  )

# Reorder columns to match final_data_september and remove hprop, fprop, nprop
sapling_survey <- sapling_survey  |> 
 left_join(final_data_september |> select(plot, subplot, site, diversity)|> distinct()) |> 
select(
    date, month, plot, subplot, site, diversity, id, species, genus, family, growth_form, survival, height,
    number_leaves, number_herb_damaged, percent_hmin, percent_hmax,
    number_fungal_damaged, percent_fmin, percent_fmax,
    number_necrotic_damaged, percent_nmin, percent_nmax, notes, type
  )
```

```{r}
str(sapling_survey)
str(final_data_september)
```

```{r}
# Get unique species from both dataframes
species_sapling <- sapling_survey |> distinct(species) |> mutate(source = "sapling_survey")
species_final <- final_data_september |> distinct(species) |> mutate(source = "final_data_september")

# Combine into one dataset
species_combined <- bind_rows(species_sapling, species_final)

# Create a summary table showing presence in each dataset
species_wide <- species_combined |>
  mutate(present = TRUE) |>
  tidyr::pivot_wider(
    names_from = source,
    values_from = present,
    values_fill = FALSE
  )

species_wide 
```

```{r}
sapling_survey
```

```{r}
# Load the required package for fill()
surveys <- final_data_september |> 
  mutate(
    species = case_when(
      str_to_lower(species) == "musseanda esquirolii" ~ "mussaenda esquirolii",
      TRUE ~ species
    ),
    date = as.Date(date),
    month = month(date), 
	  year = year(date)
  ) |> 
  select(-X) |> 
  distinct() |> 
  full_join(sapling_survey) |> 
  group_by(plot) |> 
  fill(site, diversity, .direction = "down") |> 
  ungroup()
```

```{r}
surveys <- surveys |>
  mutate(
    subplot = if_else(subplot == "aw14" & id == "1726", "aw14-i", subplot),
    percent_herb = number_herb_damaged / number_leaves,
    percent_necrose = number_necrotic_damaged / number_leaves,
    percent_fungal = number_fungal_damaged / number_leaves
  ) |>
  relocate(notes, .after = last_col())
write.csv(surveys, file = "/Users/godbergodbersen/Desktop/phd_bef_china/phd_bef_china/datas_and_notebooks/final_datas/final_surveys.csv") 
surveys
```

# Vegetation survey

```{r}
veg_2023 <- read_excel("/Users/godbergodbersen/Desktop/phd_bef_china/phd_bef_china/datas_and_notebooks/2023/may_23/Vegetation survey 2023.xlsx") |> 
  clean_names() |> 
  mutate(across(where(is.character), ~ str_trim(str_to_lower(.))))

str(veg_2023)
veg_2023
```

```{r}
veg_2024 <- read_excel("/Users/godbergodbersen/Desktop/phd_bef_china/phd_bef_china/datas_and_notebooks/2024/Vegetation survey spring 2024 (1 subplot missing).xlsx") |> 
  clean_names() |> 
  mutate(
    across(
      everything(),
      ~ {
        x_chr <- as.character(.)
        x_chr <- str_replace_all(x_chr, fixed("80 (w)"), "80")
        x_chr <- str_replace_all(x_chr, fixed("0.55000000000000004"), "0.55")
        x_chr <- str_replace_all(x_chr, fixed("7.0000000000000007e-2"), "0.07")
        x_chr <- str_replace_all(x_chr, fixed("0.56999999999999995"), "0.5699")
        x_chr <- str_replace_all(x_chr, fixed(","), ".")
        if (is.character(.)) {
          x_chr <- str_trim(str_to_lower(x_chr))
          x_chr[grepl("^na$", x_chr)] <- NA_character_
        }
        suppressWarnings(type.convert(x_chr, as.is = TRUE))
      }
    )
  )

veg_2024 <- veg_2024 |> 
  select(-c(16, 17), -c(19:ncol(veg_2024))) |> 
  mutate(
    max_herb_layer_height = as.numeric(if_else(
      max_herb_layer_height == "80 (w)", 
      "80", 
      max_herb_layer_height
    ))
  )

veg_2024_num <- veg_2024 |>
  mutate(across(
    .cols = setdiff(seq_along(veg_2024), c(1:3, 16)),
    .fns = as.numeric
  ))

# Rename columns to match veg_2023
veg_2024_num <- veg_2024_num |>
  rename(
    herb_max = max_herb_layer_height,
    herbaceous = herb,
    woody = woody_plants,
    open = open_ground,
    leaflitter = leaf_litter,
    leaflitter_depth = leaf_litter_dept,
    deadwood = deadwppd
  )

# Add missing columns (saplings, seedlings) as NA if not present
if (!"saplings" %in% names(veg_2024_num)) {
  veg_2024_num$saplings <- NA_real_
}
if (!"seedlings" %in% names(veg_2024_num)) {
  veg_2024_num$seedlings <- NA_real_
}

# Reorder columns to match veg_2023
veg_2024_num <- veg_2024_num |>
  select(
    date,  plot, subplot, tot_veg, herb_max, grass, fern, herbaceous, woody, 
    rock, deadwood, leaflitter, moss, notes
  )

# Convert date to POSIXct to match veg_2023
veg_2024_num <- veg_2024_num |>
  mutate(date = as.POSIXct(date))

str(veg_2024_num)
veg_2024_num
```

```{r}
lapply(veg_2024, unique)
```

```{r}
(veg_surveys <- veg_2023 |> 
  full_join(
    veg_2024_num |> 
      mutate(
        date = str_replace_all(date, "2023", "2024"),
        date = as.Date(date)
      )
  ) |>  
   distinct() |> 
  filter(
    !(subplot == "ao22-iii" & grass == 0.001),
    !(subplot == "aq21-iii" & grass == 0.01),
    !(subplot == "aq9-i" & tot_veg == 0.4)
  ) |> 
mutate(year = year(date)) |> 
 distinct())

write.csv(veg_surveys, "/Users/godbergodbersen/Desktop/phd_bef_china/phd_bef_china/datas_and_notebooks/final_datas/final_veg_surveys.csv")
```

```{r}
veg_surveys |>
  group_by(date, plot, subplot) |>
  summarise(n = n(), .groups = "drop") |>
  filter(n > 1)
```

# Final Join with may/sept surveys

```{r}
(final_joined <- surveys |> 
  mutate(
    year = year(date), 
    subplot = ifelse(plot == "bq27" & subplot == "bo27-iv", "bq27-iv", subplot),
    subplot = ifelse(plot == "aj21" & subplot == "ai21-ii", "aj21-ii", subplot),
    subplot = str_replace_all(subplot, " ", "")
  ) |> 
  filter(!(subplot == "bt19-iiiv" & id == "1282")) |>
  left_join(
    veg_surveys |> 
      mutate(year = year(date)) |> 
      select(-c(date, notes)) |> 
      distinct()
  )
)
write.csv(final_joined, file = "/Users/godbergodbersen/Desktop/phd_bef_china/phd_bef_china/datas_and_notebooks/final_datas/final_joined.csv")
```

ao22-ii missing
aq21-ii missing
aq9-ii missing
aq9-i.o. missing
bx21-i missing



