---
title: An R Markdown document converted from "/Users/godbergodbersen/Desktop/phd_bef_china/notebook.ipynb"
output: html_document
---

# Install and load packages 

```{r message=FALSE, warning=FALSE, include=TRUE, paged.print=TRUE}
if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}

if (!requireNamespace("corrplot", quietly = TRUE)) {
  install.packages("corrplot")
}

if (!requireNamespace("broom.mixed", quietly = TRUE)) {
  install.packages("broom.mixed")
}

if (!requireNamespace("psych", quietly = TRUE)) {
  install.packages("psych")
}

if (!requireNamespace("factoextra", quietly = TRUE)) {
  install.packages("factoextra")
}

if (!requireNamespace("ggExtra", quietly = TRUE)) {
  install.packages("ggExtra")
}

if (!requireNamespace("janitor", quietly = TRUE)) {
  install.packages("janitor")
}

if (!requireNamespace("lubridate", quietly = TRUE)) {
  install.packages("lubridate")
}

if (!requireNamespace("readr", quietly = TRUE)) {
  install.packages("readr")
}

if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

if (!requireNamespace("dplyr", quietly = TRUE)) {
  install.packages("dplyr")
}

if (!requireNamespace("viridis", quietly = TRUE)) {
  install.packages("viridis")
}

if (!requireNamespace("ggridges", quietly = TRUE)) {
  install.packages("ggridges")
}

if (!requireNamespace("sjPlot", quietly = TRUE)) {
  install.packages("sjPlot")
}

if (!requireNamespace("see", quietly = TRUE)) {
  install.packages("see")
}

if (!requireNamespace("gtsummary", quietly = TRUE)) {
  install.packages("gtsummary")
}

if (!requireNamespace("lme4", quietly = TRUE)) {
  install.packages("lme4")
}

if (!requireNamespace("performance", quietly = TRUE)) {
  install.packages("performance")
}

if (!requireNamespace("broom", quietly = TRUE)) {
  install.packages("broom")
}

if (!requireNamespace("naniar", quietly = TRUE)) {
  install.packages("naniar")
}

if (!requireNamespace("cluster", quietly = TRUE)) {
  install.packages("cluster")
}

if (!requireNamespace("fastDummies", quietly = TRUE)) {
  install.packages("fastDummies")
}

if (!requireNamespace("clValid", quietly = TRUE)) {
  install.packages("clValid") 
}

if (!requireNamespace("ggbiplot", quietly = TRUE)) {
  install.packages("ggbiplot") 
}

if (!requireNamespace("reshape2", quietly = TRUE)) {
  install.packages("reshape2") 
}

if (!requireNamespace("ggcorrplot", quietly = TRUE)) {
  install.packages("ggcorrplot") 
}

if (!requireNamespace("glmmTMB", quietly = TRUE)) {
  install.packages("glmmTMB") 
}

if (!requireNamespace("ggstatsplot", quietly = TRUE)) {
  install.packages("ggstatsplot") 
}

if (!requireNamespace("mice", quietly = TRUE)) {
  install.packages("mice") 
}

if (!requireNamespace("effects", quietly = TRUE)) {
  install.packages("effects") 
}

if (!requireNamespace("patchwork", quietly = TRUE)) {
  install.packages("patchwork") 
}

if (!requireNamespace("pheatmap", quietly = TRUE)) {
  install.packages("pheatmap") 
}

if (!requireNamespace("plotly", quietly = TRUE)) {
  install.packages("plotly") 
}

if (!requireNamespace("tidyverse", quietly = TRUE)) {
  install.packages("tidyverse") 
}

if (!requireNamespace("readxl", quietly = TRUE)) {
  install.packages("readxl") 
}


library(tidyverse)
library(readxl)
library(janitor)
```

# Data cleaning and creation of new datasets for September 2023

```{r, results="hide"}

# List all .xlsx files in the current working directory
xlsx_files <- list.files(
  path = "/Users/godbergodbersen/Desktop/phd_bef_china/phd_bef_china/datas_and_notebooks/2023/september_23", 
  pattern = "\\.xlsx$", 
  full.names = TRUE
)

# Read all .xlsx files into a named list of data frames
xlsx_data <- lapply(xlsx_files, readxl::read_excel)
names(xlsx_data) <- basename(xlsx_files)

xlsx_data
```
## Create a new dataset containing information about growth form and family of the species

```{r}
genus <- c('quercus','dalbergia','rhododendron','ilex','loropetalum','camellia','nyssa','eurya','symplocos','ardisia','buddleja','styrax',NA,'trema','musseanda','lindera','syzygium','adinandra','smilax','lithocarpus','clerodendrum','calicarpa','cinnamomum','castanea','itea','manglietia','actinidia','premna','osmanthus','alniphyllum','crataegus','schoepfia','rhaphiolepis','betula','machilus','castanopsis','photinia','litsea','distylium','euonymus','rosa','vaccinium','fraxinus','liquidambar','unknown','centaurea','pterostyrax','euscaphis','melia','rhus','not-liquidambar','viburnum','fern','albizia','rubus','phyllostachys','broussonetia','aralia','toxicodendron','ailanthus')

family <- c('Fagaceae','Fabaceae','Ericaceae','Aquifoliaceae','Hamamelidaceae','Theaceae','Nyssaceae','Pentaphylacaceae','Symplocaceae','Primulaceae','Scrophulariaceae','Styracaceae',NA,'Cannabaceae','Rubiaceae','Lauraceae','Myrtaceae','Pentaphylacaceae','Smilacaceae','Fagaceae','Lamiaceae','Lamiaceae','Lauraceae','Fagaceae','Iteaceae','Magnoliaceae','Actinidiaceae','Lamiaceae','Oleaceae','Styracaceae','Rosaceae','Schoepfiaceae','Rosaceae','Betulaceae','Lauraceae','Fagaceae','Rosaceae','Lauraceae','Hamamelidaceae','Celastraceae','Rosaceae','Ericaceae','Oleaceae','Altingiaceae',NA,'Asteraceae','Styracaceae','Staphyleaceae','Meliaceae','Anacardiaceae',NA,'Adoxaceae','Polypodiopsida','Fabaceae','Rosaceae','Poaceae','Moraceae','Araliaceae','Anacardiaceae','Simaroubaceae')

growth_form <- c('tree', 'tree', 'shrub/tree', 'shrub/tree', 'shrub', 
                 'shrub/tree', 'tree', 'shrub/tree', 'shrub/tree', 'shrub', 'shrub', 
                 'shrub/tree', 'unknown', 'tree', 'shrub/tree', 'shrub/tree', 
                 'shrub/tree', 'shrub/tree', 'liana/shrub', 'tree', 
                 'shrub/tree/vine', 'shrub/tree', 'tree', 'tree', 'shrub', 'tree', 
                 'liana', 'tree/shrub', 'shrub/tree', 'tree', 'shrub/tree', 
                 'shrub/tree', 'shrub/tree', 'tree/shrub', 'tree/shrub', 'tree', 
                 'shrub/tree', 'tree/shrub', 'shrub/tree', 'shrub/tree/liana', 
                 'shrub/liana', 'shrub/herb', 'tree', 'tree', 'unknown', 'herb', 
                 'tree/shrub', 'tree/shrub', 'tree', 'shrub/tree', 'unknown', 
                 'shrub/tree', 'herb/tree', 'tree/shrub', 'shrub/liana/herb', 
                 'shrub/tree', 'tree', 'herb/shrub/tree', 'shrub/tree/liana', 'tree')

# Erstellen des Data Frames

genus_family_df <- data.frame(genus, family, growth_form, stringsAsFactors = FALSE) |> 
  janitor::clean_names() |> 
  dplyr::mutate(family = tolower(family), growth_form = case_when(genus == "aralia" ~ "tree", genus == "clerodendrum" ~ "shrub/tree", genus == "rubus" ~ "shrub", genus == "vaccinium" ~ "shrub/tree", genus == "euonymus" ~ "shrub/tree", genus == "toxidodendron" ~ "shrub/tree",  TRUE ~ growth_form)) |> 
 mutate(growth_form = str_replace_all(growth_form, "tree/shrub", "shrub/tree"), growth_form = str_replace_all(growth_form, "liana/shrub", "shrub/liana"))
genus_family_df
```

## Cleaning process of the datasets

```{r}
# Clean column names, trim/tolower all character columns, and convert "na" strings to NA
xlsx_data <- lapply(
  xlsx_data,
  function(df) {
    df <- clean_names(df)
    df <- df %>%
      mutate(across(
        where(is.character),
        ~ {
          x <- str_trim(tolower(.))
          x[x == "na"] <- NA_character_
          x
        }
      ))
    df
  }
)
```

```{r}
# Print column names of each dataset in xlsx_data
for (name in names(xlsx_data)) {
  cat("Columns in", name, ":\n")
  print(str(xlsx_data[[name]]))
  cat("\n")
}
```

```{r}
# Find common column names across all data frames in xlsx_data
common_colnames <- Reduce(intersect, lapply(xlsx_data, colnames))
common_colnames
```

```{r}
# List all .xlsx files in the current working directory
xlsx_files <- list.files(pattern = "\\.xlsx$", full.names = TRUE)

# Read all .xlsx files into a named list of data frames
xlsx_data <- lapply(xlsx_files, read_excel)
names(xlsx_data) <- basename(xlsx_files)

# Clean column names, trim/tolower all character columns, convert "na" strings to NA,
# and replace "," between two digits with "."
xlsx_data <- lapply(
  xlsx_data,
  function(df) {
    df <- clean_names(df)
    df <- df %>%
      mutate(across(
        where(is.character),
        ~ {
          x <- str_trim(tolower(.))
          x[x == "na"] <- NA_character_
          # Replace "," between two digits with "."
          x <- str_replace_all(x, "(?<=\\d),(?=\\d)", ".")
          x
        }
      ))
    df
  }
)
```

```{r}
# Display each dataset in xlsx_data (show in notebook, not print)
xlsx_data$sapling_survey_september_2023_2.xlsx
xlsx_data$sapling_survey_september_2023_3.xlsx
xlsx_data$sapling_survey_september_2023_4.xlsx
xlsx_data$sapling_survey_september_2023_5.xlsx
#xlsx_data$sapling_survey_september_2023_2.xlsx
```

```{r}
str(xlsx_data)
```

```{r}
# Custom cleaning function for all data frames
xlsx_data <- lapply(
  xlsx_data,
  function(df) {
    df <- df %>%
      mutate(across(
        where(is.character),
        ~ {
          x <- .
          # Remove all "/"
          x <- str_replace_all(x, "/", "")
          # Replace "absent" (case-insensitive) with NA
          x[tolower(x) == "absent"] <- NA_character_
          # Replace digit followed by "b" (e.g., 0.3b) with just the digit part
          x <- str_replace_all(x, "(\\d+(?:\\.\\d+)?)b", "\\1")
          # Replace "à?à\\" with "0.01"
          x <- str_replace_all(x, "à\\?à\\\\", "0.01")
		  x <- str_replace_all(x, "à", NA_character_)
          # Replace "?" with "."
          x <- str_replace_all(x, "\\?", ".")
          # Replace " - " (space-dash-space) with "-"
          x <- str_replace_all(x, " - ", "-")
          x
        }
      ))
    df
  }
)

# Special cleaning for percent_damage_fp in sapling_survey_september_2023_5.xlsx
if ("sapling_survey_september_2023_5.xlsx" %in% names(xlsx_data)) {
  df5 <- xlsx_data[["sapling_survey_september_2023_5.xlsx"]]
  if ("percent_damage_fp" %in% names(df5)) {
    # Replace all "," with "0." in percent_damage_fp
    df5$percent_damage_fp <- str_replace_all(df5$percent_damage_fp, ",", "0.")
    xlsx_data[["sapling_survey_september_2023_5.xlsx"]] <- df5
  }
}

# Remove columns x11, x14, x17 from sapling_survey_september_2023_5.xlsx
if ("sapling_survey_september_2023_5.xlsx" %in% names(xlsx_data)) {
  df5 <- xlsx_data[["sapling_survey_september_2023_5.xlsx"]]
  cols_to_remove <- c("x11", "x14", "x17")
  df5 <- df5[, !(names(df5) %in% cols_to_remove), drop = FALSE]
  xlsx_data[["sapling_survey_september_2023_5.xlsx"]] <- df5
}

if ("sapling_survey_september_2023_4.xlsx" %in% names(xlsx_data)) {
  df4 <- xlsx_data[["sapling_survey_september_2023_4.xlsx"]]
  cols_to_remove <- c("x260")
  df4 <- df4[, !(names(df4) %in% cols_to_remove), drop = FALSE]
  xlsx_data[["sapling_survey_september_2023_4.xlsx"]] <- df5
}
```

## Joining the clean datasets into one 

```{r}
# Assuming xlsx_data is a list of dataframes
# Perform a full join of all dataframes in xlsx_data
df_full_joined <- reduce(xlsx_data, full_join)

str(df_full_joined)
```

## Fix spelling mistakes and add missing species names

```{r}
(df_full_joined_2 <- df_full_joined %>%
  mutate(
    growth_form = case_when(
      species == "fern" ~ "fern",
      species == "herb" ~ "herb",
	  species == "woody recruit" ~ "tree/shrub",
      TRUE ~ NA_character_
    )
  ) %>%
  mutate(across(where(is.character), str_trim)) %>%
  mutate(
    site = ifelse(startsWith(plot, "b"), "b", site),
    number_leaves = ifelse(
      (is.na(number_leaves) | number_leaves == "" | number_leaves == "NA") & 
      !(is.na(leaves) | leaves == "" | leaves == "NA"),
      leaves,
      number_leaves
    ),
    notes = ifelse((species == "look at photo"), "look at photo (3)", notes), 
      species = case_when(
      id == "737x" ~ "fern",
      id == "963" ~ "trema cannabina",
      id == "392" ~ "distylium buxifolium",
      species == "444" ~ "clerodendrum cyrtophyllum",
      species == "clerodendrum cyrtophyllum (444)" ~ "clerodendrum cyrtophyllum",
      species == "1171" ~ "lindera reflexa",
      species == "307" ~ "ilex suaveolens",
      id == "1294" ~ "eurya muricata", 
		  id == "1294" ~ "eurya muricata", 
		  id == "1242" ~ "pterostyrax corymbosus",
		  id == "1021" ~ "premna microphylla",
		  id == "1217" ~ "camellia fraterna",
		  id == "1390" ~ "buddleja lindleyana",
      species == "si" ~ "ilex ficoidea",
      species == "calicarpa sp" ~ "calicarpa sp.",
      species == "camellis sinensis" ~ "camellia sinensis",
      species == "camerllia sinensis" ~ "camellia sinensis", 
      species == "adinandra milletti" ~ "adinandra millettii", 
      species == "castanopsis fargesi" ~ "castanopsis fargesii", 
      species == "cinammomum camphora" ~ "cinnamomum camphora",
      species == "knoopkruid" ~ "centaurea jacea",  
      species == "lithicarpus glaber" ~ "lithocarpus glaber",  
      species == "pterostryax corymbosus" ~ "pterostyrax corymbosus",
      species == "rosa" ~ "rosa sp.",
      species == "rubus cotchotifolius" ~ "rubus corchorifolius",
      species == "schoepia jasminodora" ~ "schoepfia jasminodora",
      species == "smlax china" ~ "smilax china",
      species == "seedling (cfr. litea)" ~ "litea sp.",
      species == "xxx" ~ "unknown sp.",
      species == "fern" ~ "unknown sp.",
		  species == "herb" ~ "unknown sp.",
		  species == "tremna cannabina" ~ "trema cannabina", 
		  species == "tremna cnnabina" ~ "trema cannabina", 
		  species == "vaccinium bracetatum" ~ "vaccinium bracteatum", 
	    species == "woody recruit" ~ "unknown sp.", 
		  species ==  "styrax odoratismus" ~ "styrax odoratissimus", 
		  species ==  "styrax odoratissmus" ~ "styrax odoratissimus",
      is.na(species) ~ "unknown sp.",
      str_detect(str_to_lower(species), "buddleja") ~ "buddleja lindleyana",
      str_detect(str_to_lower(species), "rhap") ~ "rhaphiolepis indica",
      str_detect(str_to_lower(species), "rhod") ~ "rhododendron simsii",
      str_detect(str_to_lower(species), "lindera ery") ~ "lindera erythrocarpa", 
      TRUE ~ species
    ),
    # Replace only the word "seedling" (case-insensitive) with "sp." in species, not the whole cell
    species = str_replace_all(species, regex("\\bseedling\\b", ignore_case = TRUE), "sp."),
    species = str_replace_all(species, regex("\\bseediing\\b", ignore_case = TRUE), "sp."),
    species = str_replace_all(species, regex("\\bseedliing\\b", ignore_case = TRUE), "sp."),
    species = str_replace_all(species, regex("\\bseedlind\\b", ignore_case = TRUE), "sp."),
    # Fix: Use if_else to replace "sp." with NA_character_
    species = if_else(species == "sp.", NA_character_, species),
    species = if_else(species == "look at photo", NA_character_, species),
    species = str_replace_all(species, regex("fraxnus", ignore_case = TRUE), "fraxinus"),
    # Replace [euonymus maxiflorus] with "euonymus maxiflorus"
    species = str_replace_all(species, fixed("[euonymus maxiflorus]"), "euonymus maxiflorus")
  ) %>%
  mutate(
    id = case_when(
      str_to_lower(species) == "loropetalum chinense" & id == "1294" ~ "1294a",
      id == "0.14299999999999999" ~ "143",
      TRUE ~ id
    )
  ) %>%
  select(-leaves) |> 
  filter(!is.na(id)) |> 
  mutate(
    subplot = if_else(is.na(subplot) | subplot == "" | subplot == "NA", individual_id, subplot), 
    notes = if_else(is.na(notes) | notes == "" | notes == "NA", x18, notes)
  ) |> 
  select(-individual_id, -x18) |>
  group_by(plot) |>
  mutate(
    diversity = if (all(is.na(diversity))) NA_real_ else first(na.omit(diversity))
  ) |>
  ungroup())
```

```{r}
df_full_joined_2 <- df_full_joined_2 |>
  mutate(
    type = if_else(is.na(type) & notes == "seedling", notes, type), 
    species = if_else(species == "sp. (cfr. litsea)", "litsea sp.", species)
  ) |>
  filter(!(species == "ilex suaveolens" & id == "101"), !(id == "105" & number_leaves == ">75"), !(id == "1056" & number_leaves == ">75 (3)"), !(id == "1063" & number_leaves == ">75 (3)"), !(id == "1059" & number_leaves == ">75 (3)"), !(id == "107" & number_leaves == ">75 (5)")) 
df_full_joined_2
```

```{r}
# Identify columns to fill (excluding grouping columns)
group_cols <- c("species", "id", "date", "site", "plot", "subplot")
fill_cols <- setdiff(names(df_full_joined_2), group_cols)

# For each group, check if all non-NA values in each column are identical
df_full_joined_2 <- df_full_joined_2 |>
   mutate(number_leaves = str_replace_all(number_leaves, fixed(">"), NA), number_leaves = str_replace_all(number_leaves, fixed("p"), NA), number_leaves = str_replace_all(number_leaves, fixed("."), NA), notes = str_replace_all(notes, fixed("miswritten as 431 in prev census; 5"), NA), height = str_replace_all(height, fixed("dead"), NA), notes = str_replace_all(notes, fixed("previously assigned to iv by accident. 4"), NA)) |> 
  #filter(!notes == "miswritten as 431 in prev census; 5") |> 
  group_by(across(all_of(group_cols))) |>
  mutate(
    across(
      all_of(fill_cols),
      ~ {
        # Remove NAs and get unique values
        uniq_vals <- unique(na.omit(.x))
        # If only one unique non-NA value, fill NAs with it
        if (length(uniq_vals) == 1) {
          replace(.x, is.na(.x), uniq_vals)
        } else {
          .x
        }
      }
    )
  ) |>
  ungroup() |>
  distinct() 

df_full_joined_2
```

## summarise by groups and identify potential duplicates 

```{r}
# Remove specified columns
df_full_joined_2 <- df_full_joined_2 |>
  select(-c(
    number_herbivory_damaged, herb_dam_27, hprop,
    number_fungal_pathogen_damaged, fprop, number_necrosis, percent_damage_fp, number_necrose_damage, percent_damage_necrose, percent_damage_herbivory
  ))

# Define grouping columns
group_cols <- c("date", "plot", "subplot", "id", "species")

# Columns to check for similarity (excluding survival and group columns)
check_cols <- setdiff(names(df_full_joined_2), c(group_cols, "survival"))

# For each group, if all columns except survival are identical, unite survival with ";"
df_full_joined_2 <- df_full_joined_2 |>
  group_by(across(all_of(group_cols))) |>
  mutate(
    n_rows = n()
  ) |>
  mutate(
    all_equal = all(across(all_of(check_cols), ~ n_distinct(.x) == 1))
  ) |>
  mutate(
    survival = ifelse(
      all_equal,
      paste(sort(unique(survival)), collapse = ";"),
      survival
    )
  ) |>
  filter(if (first(all_equal)) row_number() == 1 else TRUE) |>
  ungroup() |>
  select(-n_rows, -all_equal) |> 
  distinct()

df_full_joined_2
```

## Join additional species information and turn columns into right format (e.g. numeric)

```{r}
(df_full_joined_2 <- df_full_joined_2 |> 
  group_by(date, plot, site, subplot, id, species, height, survival, seed_source, type, diversity) |> 
  distinct() |> 
  slice(1) |> 
  select(
    date, site, plot, subplot, diversity, id, species, 
    -status, seed_source, type, growth_form, survival, height, survival,  
    number_leaves, 
    "number_herb_damaged" = herb_dam_14, 
    "number_fungal_damaged" = fp_dam, 
    "number_necrotic_damaged" = nec_dam, 
    -prop, percent_hmin, percent_hmax, percent_fmin, percent_fmax, percent_nmin, percent_nmax, notes
  ) |> 
  mutate(
    species = ifelse(is.na(species) | species == "", "unknown sp.", species),
    genus = word(species, 1, sep = " "),
    diversity = as.numeric(diversity),
    height = as.numeric(height),
    number_leaves = as.numeric(number_leaves),
    number_herb_damaged = as.numeric(number_herb_damaged),
    number_fungal_damaged = as.numeric(number_fungal_damaged),
    number_necrotic_damaged = as.numeric(number_necrotic_damaged),
    percent_hmin = as.numeric(percent_hmin),
    percent_hmax = as.numeric(percent_hmax),
    percent_fmin = as.numeric(percent_fmin),
    percent_fmax = as.numeric(percent_fmax),
    percent_nmin = as.numeric(percent_nmin),
    percent_nmax = as.numeric(percent_nmax)
  ) |> 
  relocate(genus, .after = species) |> 
  distinct() |> 
  ungroup() |> 
  select(-growth_form) |> 
  full_join(genus_family_df) |> 
  mutate(
    family = ifelse(species == "unknown sp.", "unknown", family),
    genus = ifelse(species == "unknown sp.", "unknown", genus), 
	  growth_form = ifelse(species == "unknown sp.", "unknown", growth_form)
  ) |>
  relocate(family, .after = genus) |>
  relocate(growth_form, .after = family) |> 
  ungroup() |> 
  filter(!is.na(growth_form)) |> 
  distinct()
  )
```

## Get a last overview about the data, identify potentially mistakes worth to repair

```{r}
df_full_joined_2 |> 
  mutate(
    percentage_herb_damage = number_herb_damaged / number_leaves,
    percentage_fungal_damage = number_fungal_damaged / number_leaves,
    percentage_necrotic_damage = number_necrotic_damaged / number_leaves
  ) |>
  relocate(notes, .after = last_col())
```

```{r}
df_full_joined_2 <- df_full_joined_2 %>%
  mutate(
    seed_source_short = case_when(
      str_detect(seed_source, regex("external invader", ignore_case = TRUE)) ~ "EI",
      str_detect(seed_source, regex("planted, but not at this site|not at this site|alternate species pool", ignore_case = TRUE)) ~ "ASP",
      str_detect(seed_source, regex("internal invader", ignore_case = TRUE)) ~ "II",
      str_detect(seed_source, regex("regeneration", ignore_case = TRUE)) ~ "R",
      is.na(seed_source) | str_trim(seed_source) == "" ~ NA_character_,
      TRUE ~ seed_source
    ),
    notes = if_else(
      !is.na(notes) & str_trim(notes) != "",
      paste0(notes, "; ", seed_source),
      seed_source
    )
  ) %>%
  relocate(seed_source_short, .after = growth_form) |> 
  select(-seed_source)
df_full_joined_2
```

## write the final dataset into .csv for further usage

```{r}
write.csv(df_full_joined_2, file = "/Users/godbergodbersen/Desktop/phd_bef_china/phd_bef_china/datas_and_notebooks/2023/september_23/final_data_september.csv")
```



